other functionalities

### 2022-08-09 inst/gitbook/05_other-functionalities.Rmd
Minor updates on the gitbook
updated gitbook for 1.7

```{r}
## Loading the charadriiformes data that contains a MCMCglmm object
data(charadriiformes)]
my_MCMCglmm <- charadriiformes$posteriors

@@

```{r}
## The same plot as before without the diagonal being the maximal observed value
pair.plot(data, what = 1, col = c("orange", "blue"), legend = TRUE, diag = "max")
## Highlighting with an asterisk which squares have a value below 0.2
pair.plot(data, what = 1, binary = 0.2, add = "*", cex = 2)
```

>>>>

```{r}
## Loading the charadriiformes data that contains a MCMCglmm object
data(charadriiformes)
my_MCMCglmm <- charadriiformes$posteriors

@@

```{r}
## The same plot as before without the diagonal being
## the maximal observed value
pair.plot(data, what = 1, col = c("orange", "blue"), legend = TRUE,
          diag = "max")
## Highlighting with an asterisk which squares have a value
## below 0.2
pair.plot(data, what = 1, binary = 0.2, add = "*", cex = 2)
```
